Numerical simulation of the Cordilleran ice sheet through the last glacial cycle

### 2014-06-03 cordillera-cycle.tex
Update notes to co-authors.

\note{Please read through the abstract, introduction and figure captions. All
      other sections are very preliminary at this stage. I need some feedback
      on the (currently embryonic) discussion part.}

@@

\note{Currently, this section contains parts from the previous paper.}

@@

@@

>>>>

\begin{center}
\begin{tabular}{>{\bfseries}ll}
    \tophline
    Introduction & Happy with it except for missing refs.\\
    Model setup  & Needs minor fixes to avoid repeating the previous paper.\\
    Results      & Almost happy with it. \\
    Discussion   & Large gaps still have to be filled.\\
    Conclusions  & Main contents are here but the text needs to be improved.\\
    Figures      & I have plans for a couple extra ones.\\
    \bottomhline
\end{tabular}
\end{center}

@@

\todo{Small adjustments to avoid repetitions with the previous paper.}

@@

\todo{Develop the three subsections in order to reach the conclusions.}

@@

\todo{Improve the style.}
